Benefits and risks of diversification for individual fishers

### 2017-07-07 portfolio/text/anderson-etal-rev-pfx.tex
Tweak format for editorial office
Wrap abstract and add alternative title

\title{Benefits and risks of diversification for individual fishers}

@@

% 250:
\begin{abstract}
Individuals relying on the extraction of natural resources for their livelihood face high levels of income variability driven by a mix of environmental, biological, management, and economic factors. Key to managing these industries is identifying how regulatory actions and individual behaviour affect income variability and, by extension, economic stability and the sustainable use of natural resources. In commercial fisheries, communities and vessels fishing a greater diversity of species have less revenue variability than those fishing fewer species. However, it is unclear if these benefits extend to the actions of individual fishers and how year-to-year changes in diversification affect revenue and revenue variability. Here, we evaluate two axes by which fishers in Alaska can diversify fishing activities. We show that, despite increasing specialization over the last 30 years, fishing a set of permits with higher species diversity reduces individual revenue variability and fishing an additional permit is associated with higher revenue and lower variability. However, increasing species diversity within the constraints of existing permits has a fishery-dependent effect on revenue and is usually (87\% probability) associated with increased revenue uncertainty the following year. Our results demonstrate that the most effective option for individuals to decrease revenue variability is to participate in additional or more diverse fisheries. However, this option is expensive, often limited by regulations such as catch share programs, and consequently unavailable to many individuals. With increasing climatic variability it will be particularly important that individuals relying on natural resources for their livelihood have effective strategies to reduce income variability.
% (`r g2_dens`% probability)
\end{abstract}

@@

The fisheries data that support the findings of this study, though
confidential, are available from the Commercial Fisheries Entry
Commission (\url{https://www.cfec.state.ak.us/}) and summaries used in
this paper, along with all code, are archived in a publicly available repository at
\url{https://github.com/NCEAS/pfx-commercial/tree/master/portfolio}. } \showmatmethods

>>>>

\title{Benefits and risks of diversification for individual fishers}
% \title{Diversification trade-offs for individual fishers}

@@

% 250:
\begin{abstract}
Individuals relying on the extraction of natural resources for their livelihood
face high levels of income variability driven by a mix of environmental,
biological, management, and economic factors. Key to managing these industries
is identifying how regulatory actions and individual behaviour affect income
variability and risk and, by extension, economic stability and the sustainable use of
natural resources. In commercial fisheries, communities and vessels fishing a
greater diversity of species have less revenue variability than those fishing
fewer species. However, it is unclear if these benefits extend to the actions of
individual fishers and how year-to-year changes in diversification affect
revenue and revenue variability. Here, we evaluate two axes by which fishers in
Alaska can diversify fishing activities. We show that, despite increasing
specialization over the last 30 years, fishing a set of permits with higher
species diversity reduces individual revenue variability and fishing an
additional permit is associated with higher revenue and lower variability.
However, increasing species diversity within the constraints of existing permits
has a fishery-dependent effect on revenue and is usually (87\% probability)
associated with increased revenue uncertainty the following year. Our results
demonstrate that the most effective option for individuals to decrease revenue
variability is to participate in additional or more diverse fisheries. However,
this option is expensive, often limited by regulations such as catch share
programs, and consequently unavailable to many individuals. With increasing
climatic variability it will be particularly important that individuals relying
on natural resources for their livelihood have effective strategies to reduce
income variability.
% (`r g2_dens`% probability)
\end{abstract}

@@

The fisheries data that support the findings of this study, though
confidential, are available from the Commercial Fisheries Entry
Commission (\url{https://www.cfec.state.ak.us/}) and summaries used in
this paper, along with all code, are archived in a publicly available repository at
\url{https://github.com/NCEAS/pfx-commercial/tree/master/portfolio}.

\nocite{bates2015}
} \showmatmethods
